Results visualization across sites

### 2021-11-23 metanalysis_visualization/visualization.Rmd

```{r}
outputDir <- "../../output/latest_output/"
outputFiles <- list.files( path = outputDir, pattern = "\\.RData")
country_map <- read.delim( file = paste0( outputDir, "country_mapping.txt"))
getwd()
```

@@

>>>>

```{r}
outputDir <- "../output/latest_output/"
outputFiles <- list.files( path = outputDir, pattern = "\\.RData")
country_map <- read.delim( file = paste0( outputDir, "country_mapping.txt"))
```

@@

## Boostrap vizualisation
```{r}
names_site_id <- unique(patient_count_psy_period_psy_all$siteid)

quantile_bootstrapped_fitted_all <- bootstrapped_fitted_all %>%
  group_by(time_p, period, siteid) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = quantile(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")

annotation_function <- function(df, ...) {
  pvalue_coeff_interaction <- round(
    (1- max(
      sum(df[["periodduring_pandemic:time"]] > 0),
      sum(df[["periodduring_pandemic:time"]] < 0)
    )/nrow(df)) * 2
    , 3) 
  paste0("Coeffs differences: ",
                      round(mean(df[["periodduring_pandemic:time"]]), 2),
                      " (pvalue: ",
                      pvalue_coeff_interaction,
                      ")")
}

plot_annotations <- bootstrapped_coefficients_all %>% 
  group_by(siteid) %>% 
  group_map( annotation_function ) %>% 
  set_names(names_site_id) %>% 
  unlist()
plot_annotations_df <- data.frame(
  siteid = names(plot_annotations), 
  label = plot_annotations
)

ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("siteid", scales = "free_y") +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf, y = +Inf, hjust=0, vjust=1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all.png", height = 20, width = 32, units = "cm")
```
